Visit Scotland Notebook

### 2023-06-14 visit_scotland_notebook.Rmd
Restructured Project

```{r}
library(tidyverse)
library(here)
library(modelr)
library(ggfortify)
```

@@

demographics_all <- read_csv(here("data/clean_data/all_demographics_clean.csv"))
employment_demographics <- read_csv(here("data/clean_data/employment_demographics_clean.csv"))
gender_demographics <- read_csv(here("data/clean_data/gender_demographics_clean.csv"))
age_demographics <- read_csv(here("data/clean_data/age_demographics_clean.csv"))
marital_demographics <- read_csv(here("data/clean_data/marital_status_demographics_clean.csv"))
children_demographics <- read_csv(here("data/clean_data/children_demographics_clean.csv"))
car_demographics <- read_csv(here("data/clean_data/car_demographics_clean.csv"))
social_demographics <- read_csv(here("data/clean_data/social_demographics_clean.csv"))
regional_domestic_tourism <- read_csv(here("data/clean_data/regional_domestic_tourism_clean.csv"))
activities <- read_csv(here("data/clean_data/activities_clean.csv"))

@@

## Temporal Analysis

### Total Visits Over Time

@@

# Total Visits Over Time

demographics_all %>% 
  ggplot(aes(x = year, y = visits, group = 1)) +
  geom_line(size = 1, colour = "grey") +
  geom_point(aes(colour = visits_change_label), 
             show.legend = FALSE,
             size = 4) +
  labs(x = "\n Year",
       y = "No. of Visits (Million) \n",
       title = "Number of Visits Over Time") +
  scale_y_continuous(limits = c(0, 200), breaks = c(0, 100, 200)) +
  scale_x_continuous(breaks = c(2013, 2014, 2015, 2016, 2017, 2018, 2019))
```

### Total Expenditure Over Time

@@

# Total Expenditure Over Time

demographics_all %>% 
  ggplot(aes(x = year, y = expenditure, group = 1)) +
  geom_line(size = 1, colour = "grey") +
  geom_point(aes(colour = exp_change_label), 
             show.legend = FALSE,
             size = 4) +
  labs(x = "\n Year",
       y = "Expenditure (Million) \n",
       title = "Expenditure Over Time") +
  scale_y_continuous(limits = c(0, 6500), breaks = c(0, 2000, 4000, 6000)) +
  scale_x_continuous(breaks = c(2013, 2014, 2015, 2016, 2017, 2018, 2019))

```
### Expenditure Per Visit Over Time

@@

# Expenditure Per Visit Over Time

demographics_all %>% 
  ggplot(aes(x = year, y = exp_per_visit, group = 1)) +
  geom_line(size = 1, colour = "grey") +
  geom_point(aes(colour = exp_per_visit_label), 
             show.legend = FALSE,
             size = 4) +
  labs(x = "\n Year",
       y = "Expenditure (Millions) per Visit (Millions) \n",
       title = "Expenditure To Visit Ratio \n") +
  scale_y_continuous(limits = c(0, 60), breaks = c(0, 20, 40, 60)) +
  scale_x_continuous(breaks = c(2013, 2014, 2015, 2016, 2017, 2018, 2019))

@@

## Demographic Analysis

- Highest Mean Spend Per Visit (2013-2018) vs. 2019
- Highest Mean Spend Per Visit.

### Age

Spend Per Visit Over Period: 45-54
Spend Per Visit (2013-2018) vs. 2019: 
- Increase in 25-34, 35-44, 55-64, 65+
- Interesting decrease in 45-54 despite being highest mean across all years.

Conclusion: May suggest that there is scope for growth in other age groups, but not in 45-54.

```{r}
age_demographics %>%
  group_by(age) %>% 
  summarise(mean_exp_per_visit = mean(exp_per_visit)) %>% 
  ggplot() +
  geom_col(aes(x = reorder(age, mean_exp_per_visit), y = mean_exp_per_visit, fill = age == "45-54 years"),
           show.legend = FALSE) +
  scale_fill_manual(values = c("FALSE" = "grey40",
                               "TRUE" = "forestgreen")) +
  labs(
    x = "\n Age",
    y = "Mean Expenditure per Visit \n",
    title = "Mean Expenditure per Visit 2013-2019",
    subtitle = "By Age Group") +
  coord_flip()
```

@@

age_demographics %>% 
  mutate(is_2019 = if_else(year == 2019, "2019", "2013-2018")) %>% 
  group_by(age, is_2019) %>%
  arrange(age) %>% 
  summarise(mean_exp_per_visit = mean(exp_per_visit)) %>% 
  mutate(difference_exp_per_visit = mean_exp_per_visit - lag(mean_exp_per_visit),
         difference_exp_per_visit_pct = (mean_exp_per_visit - lag(mean_exp_per_visit)) / lag(mean_exp_per_visit) * 100,
         difference_exp_per_visit_label = if_else(difference_exp_per_visit > 0, "Increased", "Decreased")) %>% 
  filter(difference_exp_per_visit != is.na(difference_exp_per_visit)) %>% 
  ggplot(aes(x = reorder(age, difference_exp_per_visit), y = difference_exp_per_visit_pct)) +
  geom_col(aes(fill = difference_exp_per_visit_label), show.legend = FALSE) +
  # geom_text(aes(label = str_c(floor(difference_exp_per_visit_pct), "%"), vjust = -0.5)) +
  scale_fill_manual(values = c("Increased" = "forestgreen",
                               "Decreased" = "firebrick")) +
  labs(
    x = "\n Age",
    y = "% Difference \n",
    title = "Expenditure Per Visit % Difference, 2019 vs. 2013-2018 Avg.") +
  coord_flip() +
  scale_y_continuous(labels = scales::percent_format(scale = 1))

@@

### Gender

Highest Mean Spend Per Visit Over Period: Little difference between male and female spend per visit.
Mean Spend Per Visit (2013-2018) vs. 2019: Both Increased.

Conclusion: Little difference between genders, both show potential for growth.

```{r}
gender_demographics %>%
  group_by(gender) %>% 
  summarise(mean_exp_per_visit = mean(exp_per_visit)) %>% 
  ggplot() +
  geom_col(aes(x = gender, y = mean_exp_per_visit, fill = gender == "Male"),
           show.legend = FALSE) +
  scale_fill_manual(values = c("FALSE" = "grey40",
                               "TRUE" = "forestgreen")) +
  labs(
    x = "\n Gender",
    y = "Mean Expenditure per Visit \n",
    title = "Mean Expenditure per Visit 2013-2019")
```

```{r}
gender_demographics %>% 
  mutate(is_2019 = if_else(year == 2019, "2019", "2013-2018")) %>% 
  group_by(gender, is_2019) %>%
  summarise(mean_exp_per_visit = mean(exp_per_visit)) %>% 
  mutate(difference_exp_per_visit = mean_exp_per_visit - lag(mean_exp_per_visit),
         difference_exp_per_visit_pct = (mean_exp_per_visit - lag(mean_exp_per_visit)) / lag(mean_exp_per_visit) * 100,
         difference_exp_per_visit_label = if_else(difference_exp_per_visit > 0, "Increased", "Decreased")) %>% 
  filter(difference_exp_per_visit != is.na(difference_exp_per_visit)) %>% 
  ggplot(aes(x = gender, y = difference_exp_per_visit_pct)) +
  geom_col(aes(fill = difference_exp_per_visit_label), show.legend = FALSE) +
  # geom_text(aes(label = str_c(floor(difference_exp_per_visit_pct), "%"), vjust = -0.5)) +
  scale_fill_manual(values = c("Increased" = "forestgreen",
                               "Decreased" = "firebrick")) +
  labs(
    x = "\n Gender",
    y = "% Difference \n",
    title = "Expenditure Per Visit % Difference, 2019 vs. 2013-2018 Avg.") +
  scale_y_continuous(labels = scales::percent_format(scale = 1))
```

### Marital Status

Highest Mean Spend Per Visit Over Period: Married people spend more than un-married.
Mean Spend Per Visit (2013-2018) vs. 2019: Both Increased.

Conclusion: Although married people were already spending the most per visit, their spend increased by a larger amount in 2019 than un-married people, suggesting there is still plenty of room for growth.

```{r}
marital_demographics %>%
  group_by(marital_status) %>% 
  summarise(mean_exp_per_visit = mean(exp_per_visit)) %>% 
  ggplot() +
  geom_col(aes(x = marital_status, y = mean_exp_per_visit, fill = marital_status == "Married"),
           show.legend = FALSE) +
  scale_fill_manual(values = c("FALSE" = "grey40",
                               "TRUE" = "forestgreen")) +
  labs(
    x = "\n Marital Status",
    y = "Mean Expenditure per Visit \n",
    title = "Mean Expenditure per Visit 2013-2019",
    subtitle = "By Marital Status")
```

```{r}
marital_demographics %>% 
  mutate(is_2019 = if_else(year == 2019, "2019", "2013-2018")) %>% 
  group_by(marital_status, is_2019) %>%
  summarise(mean_exp_per_visit = mean(exp_per_visit)) %>% 
  mutate(difference_exp_per_visit = mean_exp_per_visit - lag(mean_exp_per_visit),
         difference_exp_per_visit_pct = (mean_exp_per_visit - lag(mean_exp_per_visit)) / lag(mean_exp_per_visit) * 100,
         difference_exp_per_visit_label = if_else(difference_exp_per_visit > 0, "Increased", "Decreased")) %>% 
  filter(difference_exp_per_visit != is.na(difference_exp_per_visit)) %>% 
  ggplot(aes(x = marital_status, y = difference_exp_per_visit_pct)) +
  geom_col(aes(fill = difference_exp_per_visit_label), show.legend = FALSE) +
  # geom_text(aes(label = str_c(floor(difference_exp_per_visit_pct), "%"), vjust = -0.5)) +
  scale_fill_manual(values = c("Increased" = "forestgreen",
                               "Decreased" = "firebrick")) +
  labs(
    x = "\n Marital Status",
    y = "% Difference \n",
    title = "Expenditure Per Visit % Difference, 2019 vs. 2013-2018 Avg.") +
  scale_y_continuous(labels = scales::percent_format(scale = 1))
```

### Children

Highest Mean Spend Per Visit Over Period: People with children spent more per visit than people without.
Mean Spend Per Visit (2013-2018) vs. 2019: Both Increased.

Conclusion: Although people with children spend more per visit than people without, both categories increased spending per visit in 2019 suggesting there is room for growth in both areas.

```{r}
children_demographics %>%
  group_by(children) %>% 
  summarise(mean_exp_per_visit = mean(exp_per_visit)) %>% 
  ggplot() +
  geom_col(aes(x = children, y = mean_exp_per_visit, fill = children == "Yes - Children"),
           show.legend = FALSE) +
  scale_fill_manual(values = c("FALSE" = "grey40",
                               "TRUE" = "forestgreen")) +
  labs(
    x = "\n Children",
    y = "Mean Expenditure per Visit \n",
    title = "Mean Expenditure per Visit 2013-2019",
    subtitle = "By Children")
```

```{r}
children_demographics %>% 
  mutate(is_2019 = if_else(year == 2019, "2019", "2013-2018")) %>% 
  group_by(children, is_2019) %>%
  summarise(mean_exp_per_visit = mean(exp_per_visit)) %>% 
  mutate(difference_exp_per_visit = mean_exp_per_visit - lag(mean_exp_per_visit),
         difference_exp_per_visit_pct = (mean_exp_per_visit - lag(mean_exp_per_visit)) / lag(mean_exp_per_visit) * 100,
         difference_exp_per_visit_label = if_else(difference_exp_per_visit > 0, "Increased", "Decreased")) %>% 
  filter(difference_exp_per_visit != is.na(difference_exp_per_visit)) %>% 
  ggplot(aes(x = children, y = difference_exp_per_visit_pct)) +
  geom_col(aes(fill = difference_exp_per_visit_label), show.legend = FALSE) +
  # geom_text(aes(label = str_c(floor(difference_exp_per_visit_pct), "%"), vjust = -0.5)) +
  scale_fill_manual(values = c("Increased" = "forestgreen",
                               "Decreased" = "firebrick")) +
  labs(
    x = "\n Children",
    y = "% Difference \n",
    title = "Expenditure Per Visit % Difference, 2019 vs. 2013-2018 Avg.") +
  scale_y_continuous(labels = scales::percent_format(scale = 1))
```

### Employment

Highest Mean Spend Per Visit Over Period: People in employment have the highest average spend per visit.
Mean Spend Per Visit (2013-2018) vs. 2019: All Increased.

Conclusion: Although people in employment have the highest spend per visit there was rleatively little growth in this area in 2019. By comparison both other categories increase their spend per visit suggesting theire is potential for growth in these areas.

```{r}
employment_demographics %>%
  group_by(employment_status) %>% 
  summarise(mean_exp_per_visit = mean(exp_per_visit)) %>% 
  ggplot() +
  geom_col(aes(x = employment_status, y = mean_exp_per_visit, fill = employment_status == "Employed/self-employed (full or part time)"),
           show.legend = FALSE) +
  scale_fill_manual(values = c("FALSE" = "grey40",
                               "TRUE" = "forestgreen")) +
  labs(
    x = "\n Employment",
    y = "Mean Expenditure per Visit \n",
    title = "Mean Expenditure per Visit 2013-2019",
    subtitle = "By Employment")
```

```{r}
employment_demographics %>% 
  mutate(is_2019 = if_else(year == 2019, "2019", "2013-2018")) %>% 
  group_by(employment_status, is_2019) %>%
  summarise(mean_exp_per_visit = mean(exp_per_visit)) %>% 
  mutate(difference_exp_per_visit = mean_exp_per_visit - lag(mean_exp_per_visit),
         difference_exp_per_visit_pct = (mean_exp_per_visit - lag(mean_exp_per_visit)) / lag(mean_exp_per_visit) * 100,
         difference_exp_per_visit_label = if_else(difference_exp_per_visit > 0, "Increased", "Decreased")) %>% 
  filter(difference_exp_per_visit != is.na(difference_exp_per_visit)) %>% 
  ggplot(aes(x = reorder(employment_status, difference_exp_per_visit_pct), y = difference_exp_per_visit_pct)) +
  geom_col(aes(fill = difference_exp_per_visit_label), show.legend = FALSE) +
  # geom_text(aes(label = str_c(floor(difference_exp_per_visit_pct), "%"), vjust = -0.5)) +
  scale_fill_manual(values = c("Increased" = "forestgreen",
                               "Decreased" = "firebrick")) +
  labs(
    x = "\n Employment Status",
    y = "% Difference \n",
    title = "Expenditure Per Visit % Difference, 2019 vs. 2013-2018 Avg.") +
  coord_flip() +
  scale_y_continuous(labels = scales::percent_format(scale = 1))

### Car Access

Highest Mean Spend Per Visit Over Period: People with access to a car spent more per visit on average.
Mean Spend Per Visit (2013-2018) vs. 2019: Both Increased.

Conclusion: Although people with access to a car spend more per visit, spend per visit amongst those without access to a car increased by more than those with a car. Highlights potential growth in this areas and particuarly related to transport.

```{r}
car_demographics %>%
  group_by(access_to_car) %>% 
  summarise(mean_exp_per_visit = mean(exp_per_visit)) %>% 
  ggplot() +
  geom_col(aes(x = access_to_car, y = mean_exp_per_visit, fill = access_to_car == "Access to car (1+)"),
           show.legend = FALSE) +
  scale_fill_manual(values = c("FALSE" = "grey40",
                               "TRUE" = "forestgreen")) +
  labs(
    x = "\n Car Access",
    y = "Mean Expenditure per Visit \n",
    title = "Mean Expenditure per Visit 2013-2019",
    subtitle = "By Car Access")
```
```{r}
car_demographics %>% 
  mutate(is_2019 = if_else(year == 2019, "2019", "2013-2018")) %>% 
  group_by(access_to_car, is_2019) %>%
  summarise(mean_exp_per_visit = mean(exp_per_visit)) %>% 
  mutate(difference_exp_per_visit = mean_exp_per_visit - lag(mean_exp_per_visit),
         difference_exp_per_visit_pct = (mean_exp_per_visit - lag(mean_exp_per_visit)) / lag(mean_exp_per_visit) * 100,
         difference_exp_per_visit_label = if_else(difference_exp_per_visit > 0, "Increased", "Decreased")) %>% 
  filter(difference_exp_per_visit != is.na(difference_exp_per_visit)) %>% 
  ggplot(aes(x = access_to_car, y = difference_exp_per_visit_pct)) +
  geom_col(aes(fill = difference_exp_per_visit_label), show.legend = FALSE) +
  # geom_text(aes(label = str_c(floor(difference_exp_per_visit_pct), "%"), vjust = -0.5)) +
  scale_fill_manual(values = c("Increased" = "forestgreen",
                               "Decreased" = "firebrick")) +
  labs(
    x = "\n Access To Car",
    y = "% Difference \n",
    title = "Expenditure Per Visit % Difference, 2019 vs. 2013-2018 Avg.") +
  scale_y_continuous(labels = scales::percent_format(scale = 1))
```

### Social Grade

AB	Higher & intermediate managerial, administrative, professional occupations.
C1	Supervisory, clerical & junior managerial, administrative, professional occupations.
C2	Skilled manual occupations.
DE	Semi-skilled & unskilled manual occupations, Unemployed and lowest grade occupations.

```{r}
social_demographics %>%
  group_by(social_grade) %>% 
  summarise(mean_exp_per_visit = mean(exp_per_visit)) %>% 
  ggplot() +
  geom_col(aes(x = reorder(social_grade, mean_exp_per_visit), y = mean_exp_per_visit, fill = social_grade == "AB"),
           show.legend = FALSE) +
  scale_fill_manual(values = c("FALSE" = "grey40",
                               "TRUE" = "forestgreen")) +
  labs(
    x = "\n Social Gradee",
    y = "Mean Expenditure per Visit \n",
    title = "Mean Expenditure per Visit 2013-2019") +
  coord_flip()
```

```{r}
social_demographics %>% 
  mutate(is_2019 = if_else(year == 2019, "2019", "2013-2018")) %>% 
  group_by(social_grade, is_2019) %>%
  summarise(mean_exp_per_visit = mean(exp_per_visit)) %>% 
  mutate(difference_exp_per_visit = mean_exp_per_visit - lag(mean_exp_per_visit),
         difference_exp_per_visit_pct = (mean_exp_per_visit - lag(mean_exp_per_visit)) / lag(mean_exp_per_visit) * 100,
         difference_exp_per_visit_label = if_else(difference_exp_per_visit > 0, "Increased", "Decreased")) %>% 
  filter(difference_exp_per_visit != is.na(difference_exp_per_visit)) %>% 
  ggplot(aes(x = reorder(social_grade, difference_exp_per_visit_pct), y = difference_exp_per_visit_pct)) +
  geom_col(aes(fill = difference_exp_per_visit_label), show.legend = FALSE) +
  # geom_text(aes(label = str_c(floor(difference_exp_per_visit_pct), "%"), vjust = -0.5)) +
  scale_fill_manual(values = c("Increased" = "forestgreen",
                               "Decreased" = "firebrick")) +
  labs(
    x = "\n Social Grade",
    y = "% Difference \n",
    title = "Expenditure Per Visit % Difference, 2019 vs. 2013-2018 Avg.") +
  coord_flip() +
  scale_y_continuous(labels = scales::percent_format(scale = 1))
```

## Domestic & International Visitors

### Domestic vs. International

```{r}
domestic_2017_2019_visits <- regional_domestic_tourism %>% 
  filter(date_code == "2017-2019",
         region_of_residence == "All of GB") %>% 
  select(visits)

international_2017_2019_visits <- international_visits %>%
  select(-c(quarter, age, sample)) %>%
  filter(year %in% c(2017, 2018, 2019)) %>% 
  summarise(total_visits = sum(visits)) %>% 
  select(total_visits)

tibble(a = c("Domestic", "International"),
       b = c(domestic_2017_2019_visits$visits, international_2017_2019_visits$total_visits)) %>% 
  ggplot() +
  geom_col(aes(x = a, y = b)) +
  labs(
    x = "",
    y = "Visits \n",
    title = "Domestic vs. International Visits",
    subtitle = "2017-2019")
```

```{r}
domestic_2017_2019_spend <- regional_domestic_tourism %>% 
  filter(date_code == "2017-2019",
         region_of_residence == "All of GB") %>% 
  select(expenditure)

international_2017_2019_spend <- international_visits %>%
  select(-c(quarter, age, sample)) %>%
  filter(year %in% c(2017, 2018, 2019)) %>% 
  summarise(total_visits = sum(visits),
            total_spend = sum(spend),
            exp_per_visit = total_spend / total_visits) %>% 
  select(total_spend)

tibble(a = c("Domestic", "International"),
       b = c(domestic_2017_2019_spend$expenditure, international_2017_2019_spend$total_spend)) %>% 
  ggplot() +
  geom_col(aes(x = a, y = b)) +
  labs(
    x = "",
    y = "Expenditure \n",
    title = "Domestic vs. International Expenditure",
    subtitle = "2017-2019")
```

### International

#### Summary

```{r}
ips_2002_2019 %>%
  summarise(cor(spend, visits))
```

```{r}
model_ips <- lm(formula = spend ~ visits, data = ips_2002_2019)
summary(model_ips)
```

```{r}
autoplot(model_ips)
```

```{r}
ips_2002_2019 %>%
  add_predictions(model_ips) %>%
  add_residuals(model_ips) %>% 
  ggplot(aes(x = visits, y = spend)) +
  geom_point() +
  geom_line(aes(y = pred), col = "red") +
  annotate("text", x = 1675, y = 2500, label = "spend ~ visits") +
  annotate("text", x = 1930, y = 2300, label = "b1 = 0.81800 / p-value = 2.46e-08") +
  annotate("text", x = 2170, y = 2100, label = "R-Squared = 0.864 / Residual Standard Error: 195.2") +
  labs(
    x = "Visits (Million)",
    y = "Expenditure (£Million) \n",
    title = "Scotland: International Visits vs. Spend",
    subtitle = "2002-2019")
```

#### By Country

```{r}
international_visits %>% 
  select(-c(quarter, age, sample)) %>%
  filter(country %in% c("USA", "Germany", "Australia", "France", "China"),
         year %in% c(2013, 2014, 2015, 2016, 2017, 
                                2018, 2019)) %>% 
  group_by(year, country) %>% 
  summarise(total_spend = sum(spend)) %>% 
  ggplot(aes(x = year, y = total_spend, colour = country)) +
  geom_line() +
  geom_point() +
  scale_x_continuous(breaks = c(2013, 2014, 2015, 2016, 2017, 
                                2018, 2019)) +
  labs(x = "\n Year",
       y = "Expenditure (Million) \n",
       title = "Expenditure by Country",
       subtitle = "Top 5 Countries per Total Expenditure")
```

```{r}
international_visits %>% 
  select(-c(quarter, age, sample)) %>%
  filter(country %in% c("USA", "Germany", "France", "Netherlands", "Australia"),
         year %in% c(2013, 2014, 2015, 2016, 2017, 
                                2018, 2019)) %>% 
  group_by(year, country) %>% 
  summarise(total_visits = sum(visits)) %>% 
  ggplot(aes(x = year, y = total_visits, colour = country)) +
  geom_line() +
  geom_point() +
  scale_x_continuous(breaks = c(2013, 2014, 2015, 2016, 2017, 
                                2018, 2019)) +
  labs(x = "\n Year",
       y = "Visits (Million) \n",
       title = "Visits by Country",
       subtitle = "Top 5 Countries per Visits")
```

#### USA

```{r}
ips_2002_2019_usa %>%
  summarise(cor(spend, visits))
```

```{r}
model_ips_usa <- lm(formula = spend ~ visits, data = ips_2002_2019_usa)
summary(model_ips_usa)
```

Model: spend ~ visits

Interpretation: ~83% of the variation in expenditure can be explained by the number of visits.

Question: USA visits increased by 11.5789% between 2018 and 2019 to 636 Million. If this percentage increase in visits was replicated in 2020 (709.642m), what would our model predict for expenditure?

Answer: If USA visits were increased as above, the model would predict expenditure of ~£723m (Low Estimate ~£655m, High Estimate ~£791m)

As calculated below.

Step 1.
outcome = b0 + b1 * 1st Predictor

Step 2.
expenditure = b0(intercept) + b1(coefficient) * 1st Predictor

Step 3.
expenditure = b0(intercept) + b1(coefficient) * `visits`

Step 4.
expenditure = -195.9631 + 1.2953 * `709.642`

Step 5.
expenditure = 723.2287 (Low Estimate 655.3287, High Estimate 791.1287)

predict_at <- data.frame(visits = c(709.642))

# get predicted heights at those sample_weights
predict(model_ips_usa, newdata = predict_at)
```

```{r}
723.2287  + c(-67.9, 67.9)
```

```{r}
ips_2002_2019_usa %>%
  add_predictions(model_ips_usa) %>%
  add_residuals(model_ips_usa) %>% 
  ggplot(aes(x = visits, y = spend)) +
  geom_point() +
  geom_line(aes(y = pred), col = "red") +
  labs(
    x = "Visits (Million)",
    y = "Expenditure (£Million) \n",
    title = "Scotland: USA Visits vs. Spend",
    subtitle = "2002-2019")
```

```{r}
autoplot(model_ips_usa)
```

### Domestic

>>>>

```{r}
library(tidyverse)
library(here)
library(sf)
library(infer)
```

@@

regional_domestic_tourism_all <- read_csv(here("data/clean_data/regional_domestic_tourism_all_clean.csv"))
regional_domestic_tourism_individual <- read_csv(here("data/clean_data/regional_domestic_tourism_individual_clean.csv"))
local_authority_geo <- st_read(dsn = "data/geo_data/", layer = "pub_las")

@@

## Trends Over Time

### Domestic Tourism / Visits

@@

regional_domestic_tourism_all %>%
  ggplot(aes(x = date_code, y = visits)) +
  geom_line(group = 1) +
  geom_point(aes(colour = visits_change_label), 
             show.legend = FALSE,
             size = 4) +
  labs(x = "\n Year Range",
       y = "Visitors (Thousands) \n",
       title = "Average Annual Number of Domestic Vistors",
       subtitle = "3 Year Average")

### Domestic Tourism / Expenditure

@@

regional_domestic_tourism_all %>%
  ggplot(aes(x = date_code, y = expenditure)) +
  geom_line(group = 1) +
  geom_point(aes(colour = exp_change_label), 
             show.legend = FALSE,
             size = 4) +
  labs(x = "\n Year Range",
       y = "Expenditure (Million GBP) \n",
       title = "Average Annual Expenditure of Domestic Vistors",
       subtitle = "3 Year Average")

```
### Domestic Tourism / Nights Stayed

@@

regional_domestic_tourism_all %>%
  ggplot(aes(x = date_code, y = nights)) +
  geom_line(group = 1) +
  geom_point(aes(colour = nights_change_label), 
             show.legend = FALSE,
             size = 4) +
  labs(x = "\n Year Range",
       y = "Nights (Thousands) \n",
       title = "Average Annual Nights Stayed by Domestic Vistors",
       subtitle = "3 Year Average")

@@

### Domestic Tourism / Expenditure per Visit

```{r}
regional_domestic_tourism_all %>%
  ggplot(aes(x = date_code, y = exp_per_visit)) +
  geom_line(group = 1) +
  geom_point(aes(colour = exp_per_visit_label), 
             show.legend = FALSE,
             size = 4) +
  labs(x = "\n Year Range",
       y = "3x Year Average Expenditure per Visit (Thousands) \n",
       title = "Average Expenditure Per Visit Domestic Vistors",
       subtitle = "3 Year Average")
```

### Which Regions Are Domestic Tourists Visiting

#### Average Visits By Region

##### Stats

@@

regional_domestic_tourism_all %>% 
  summarise(mean_annual_visits = mean(visits))

# Mean Annual Visits: ~12,337,000

regional_domestic_tourism_all %>%
  rep_sample_n(size = 12, replace = TRUE, reps = 5000) %>%
  summarise(mean_visits = mean(visits)) %>% 
  get_confidence_interval(level = 0.95, type = "percentile")

# 95% CI: 12,175,250 - 12,507,590
```

##### Map

regional_data_joined %>% 
  group_by(year, code) %>% 
  summarise(mean_visits = mean(visits)) %>% 
  ggplot(aes(fill = mean_visits)) + 
  geom_sf() +
  labs(
    x = "Longitude",
    y = "Latitude",
    title = "Average Annual Number of Domestic Vistors",
    subtitle = "By Region",
    fill = "Visits (Thousands)"
  ) +
  theme(panel.background = element_rect(fill = "white"))

@@

#### Expenditure by Region

##### Stats

```{r}
regional_domestic_tourism_all %>% 
  summarise(mean_annual_exp = mean(expenditure))

# Mean Annual Expenditure:

regional_domestic_tourism_all %>%
  rep_sample_n(size = 12, replace = TRUE, reps = 5000) %>%
  summarise(mean_annual_exp = mean(expenditure)) %>% 
  get_confidence_interval(level = 0.95, type = "percentile")

# 95% CI: 1
```

##### Map

```{r}
regional_data_joined %>% 
  group_by(year, code) %>% 
  summarise(mean_exp = mean(expenditure)) %>% 
  ggplot(aes(fill = mean_exp)) + 
  geom_sf() +
  labs(
    x = "Longitude",
    y = "Latitude",
    title = "Average Annual Expenditure of Domestic Vistors",
    subtitle = "By Region",
    fill = "Expenditure (Million GBP)"
  ) +
  theme(panel.background = element_rect(fill = "white"))
```

### Line Plot Over Time
